Yeast RNA-seq 48 sample simulation study

### 2018-05-31 datasets/RNA-Seq/yeast-simulation.Rmd
Add qqplot diagnostics for FDRreg

```{r}
#' @param X simnumber
#' @param seed random seed
#' @param dds is the full DESeq2 dataset
#' @param resFULL is the results object from running DESeq2 on dds (used in
#'   to obtain the fold change effect sizes when adding non-null genes)
#' @param sampleSize is the number of samples in each condition
#' @param nDE is the number of DE genes
#' @param bd is the bench design object
#' @param BPPARAM is the BiocParallel bpparam argument to pass to DESeq. Since
#'  parallelization happens by forking multiple instances of this function, we 
#'  will specify only one worker per DEseq intance.
#' @param uninformativeCovariate logical indicating whether to replace overall mean 
#'  independent covariate with a randomly generated (uninformative) covariate. 
#'  Default is FALSE.
simulateOneSplit <- function(X, rseed, dds, resFULL, nDE, sampleSize,
                             bd, uninformativeCovariate = FALSE){

@@

@@

if (!file.exists(resfile_n5)){
  null5 <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd)
  saveRDS(null5, file = resfile_n5)
}else{
  null5 <- readRDS(file = resfile_n5)
}
```

@@

if (!file.exists(resfile_n10)){
  null10 <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd)
  saveRDS(null10, file = resfile_n10)
}else{
  null10 <- readRDS(file = resfile_n10)
}
```

@@

if (!file.exists(resfile_d5)){
  de5 <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd)
  saveRDS(de5, file = resfile_d5)
}else{
  de5 <- readRDS(file = resfile_d5)
}
```

@@

if(!file.exists(resfile_d10)){
  de10 <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd)
  saveRDS(de10, file = resfile_d10)
}else{
  de10 <- readRDS(file = resfile_d10)
}
```

>>>>

```{r}
#' @param X simnumber
#' @param seed random seed
#' @param dds is the full DESeq2 dataset
#' @param resFULL is the results object from running DESeq2 on dds (used in
#'   to obtain the fold change effect sizes when adding non-null genes)
#' @param sampleSize is the number of samples in each condition
#' @param nDE is the number of DE genes
#' @param bd is the bench design object
#' @param BPPARAM is the BiocParallel bpparam argument to pass to DESeq. Since
#'  parallelization happens by forking multiple instances of this function, we 
#'  will specify only one worker per DEseq intance.
#' @param uninformativeCovariate logical indicating whether to replace overall mean 
#'  independent covariate with a randomly generated (uninformative) covariate. 
#'  Default is FALSE.
#' @param qq logical whether to return qqplot of test statistics (for diagnosing
#'  problems with Scott method)
simulateOneSplit <- function(X, rseed, dds, resFULL, nDE, sampleSize,
                             bd, uninformativeCovariate = FALSE, qq = FALSE){

@@

  if(qq){
    return(ggplot(data.frame(resTEST), aes(sample = stat)) + 
             geom_qq() +
             geom_abline())
  }

@@

if (!file.exists(resfile_n5)){
  null5 <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd)
  saveRDS(null5, file = resfile_n5)
}else{
  null5 <- readRDS(file = resfile_n5)
}

# qqplots
plotfile <- file.path(datdir, "null5_qqplots.pdf")
if (!file.exists(plotfile)){
  qqs <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd, 
                   qq =TRUE)
  failed <- ifelse(sapply(null5, 
                          function(x) sum(is.na(assays(x)$qvalue[,22])) > 0),
                   "Failed", "OK")
  pdf(plotfile, width=4, height=4)
  for(i in 1:length(qqs)){
    print(qqs[[i]] +
      ggtitle(paste0(failed[i])))
  }
  dev.off()
}
```

@@

if (!file.exists(resfile_n10)){
  null10 <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd)
  saveRDS(null10, file = resfile_n10)
}else{
  null10 <- readRDS(file = resfile_n10)
}

# qqplots
plotfile <- file.path(datdir, "null10_qqplots.pdf")
if (!file.exists(plotfile)){
  qqs <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd, 
                   qq =TRUE)
  failed <- ifelse(sapply(null5, 
                          function(x) sum(is.na(assays(x)$qvalue[,22])) > 0),
                   "Failed", "OK")
  pdf(plotfile, width=4, height=4)
  for(i in 1:length(qqs)){
    print(qqs[[i]] +
      ggtitle(paste0(failed[i])))
  }
  dev.off()
}
```

@@

if (!file.exists(resfile_d5)){
  de5 <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd)
  saveRDS(de5, file = resfile_d5)
}else{
  de5 <- readRDS(file = resfile_d5)
}

# qqplots
plotfile <- file.path(datdir, "de5_qqplots.pdf")
if (!file.exists(plotfile)){
  qqs <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd, 
                   qq =TRUE)
  failed <- ifelse(sapply(null5, 
                          function(x) sum(is.na(assays(x)$qvalue[,22])) > 0),
                   "Failed", "OK")
  pdf(plotfile, width=4, height=4)
  for(i in 1:length(qqs)){
    print(qqs[[i]] +
      ggtitle(paste0(failed[i])))
  }
  dev.off()
}
```

@@

if(!file.exists(resfile_d10)){
  de10 <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd)
  saveRDS(de10, file = resfile_d10)
}else{
  de10 <- readRDS(file = resfile_d10)
}

# qqplots
plotfile <- file.path(datdir, "de10_qqplots.pdf")
if (!file.exists(plotfile)){
  qqs <- bplapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd, 
                   qq =TRUE)
  failed <- ifelse(sapply(null5, 
                          function(x) sum(is.na(assays(x)$qvalue[,22])) > 0),
                   "Failed", "OK")
  pdf(plotfile, width=4, height=4)
  for(i in 1:length(qqs)){
    print(qqs[[i]] +
      ggtitle(paste0(failed[i])))
  }
  dev.off()
}
```
